Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude

### 2016-07-10 RMS/responses.tex
modified a bit

This paper has been revised according to reviewers comments and
suggestions, I recommend to accept it for publication after minor
revisions on possible typos, such as the word "monus" on page 9 and
10.

@@

\hide{
% use section* for acknowledgment
\ifCLASSOPTIONcompsoc
  % The Computer Society usually uses the plural form
  \section*{Acknowledgments}
\else
  % regular IEEE prefers the singular form
  \section*{Acknowledgment}
\fi

The authors would like to thank...
}

>>>>

This paper has been revised according to reviewers comments and
suggestions, I recommend to accept it for publication after minor
revisions on possible typos, such as the word ``monus'' on page 9 and
10.

@@

### 2016-07-10 RMS/submission.tex
complete responses to reviewer 2
modified a bit

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

@@

In this paper, we only consider Real-Time Maude's \emph{Linear
  Temporal Logic (LTL) model checker}, which analyzes whether
\emph{each} behavior satisfies a temporal logic formula. \emph{State
  propositions} are defined as terms of sort \verb|Prop|. Their
semantics is defined by conditional equations of the form $\texttt{ceq
} statePattern \texttt{ |= } prop \texttt{ = } b \texttt{ if } cond$,
with $b$ a term of sort \verb|Bool|, stating that $prop$ evaluates to
$b$ in states which are instances of $statePattern$ provided the
condition $cond$ holds. These equations together define $prop$ to hold
in all states $s$ that make $s \texttt{ |= } prop$ evaluate to
\verb|true|. A temporal logic \emph{formula} is constructed by state
propositions and temporal logic operators such as \verb|~|(negation),
\verb|\/|(or), \verb|[]|(``always'') and
\verb|U|(``until''). Real-Time Maude supports both \emph{timed} and
\emph{untimed LTL model checking}. The untimed model checking command
\begin{alltt}
  (mc \(s\) |=u \(\Phi\) .)
\end{alltt}
checks whether the temporal logic formula $\Phi$ holds in all
behaviors starting from the initial state $s$, \emph{with no time
  limit}.

@@

Time-robustness is a set of properties expected from a well-behaved
real-time rewrite theory. We avoid introducing the accurate definition
of time-robustness, but instead give the following lemma to prove
time-robustness:
\begin{lemma}[\cite{DBLP:journals/entcs/OlveczkyM07a}]
\label{l:timerobustness}
Let $\cal R$ be an object-oriented specification with a standard tick
rule, and let the infinity element \verb|INF| be the only element in
the time domain which is not a normal time value.
%and let the time domain be \emph{linear}.
Then $\cal R$ is time-robust if the following conditions are satisfied
for all appropriate ground terms $t$ and $r,r'$:
\begin{enumerate}
\item
[(i)] \verb|mte(delta(|$t$\verb|,|$r$\verb|))| $=$
\verb|mte(|$t$\verb|) monus |$r$, for all $r\le$
\verb|mte(|$t$\verb|)|, where \verb|monus| is the minus operation
defined on sort \verb|Time|;

>>>>

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

@@

In this paper, we only consider Real-Time Maude's \emph{Linear
  Temporal Logic (LTL) model checker}, which analyzes whether
\emph{each} behavior satisfies a temporal logic formula. \emph{State
  propositions} are defined as terms of sort \verb|Prop|. Their
semantics is defined by conditional equations of the form $\texttt{ceq
} statePattern \texttt{ |= } prop \texttt{ = } b \texttt{ if } cond$,
with $b$ a term of sort \verb|Bool|, stating that $prop$ evaluates to
$b$ in states which are instances of $statePattern$ provided the
condition $cond$ holds. These equations together define $prop$ to hold
in all states $s$ that make $s \texttt{ |= } prop$ evaluate to
\verb|true|. A temporal logic \emph{formula} is constructed by state
propositions and \hl{temporal logic operators such as} \verb|~|\hl{(negation),}
\verb|\/|\hl{(disjunction),} \verb|[]|\hl{(``always''),}
\verb|U|\hl{(``until'')}. Real-Time Maude supports both \emph{timed} and
\emph{untimed LTL model checking}. The untimed model checking command
\begin{alltt}
  (mc \(s\) |=u \(\Phi\) .)
\end{alltt}
checks whether the temporal logic formula $\Phi$ holds in all
behaviors starting from the initial state $s$, \emph{with no time
  limit}.

@@

Time-robustness is a set of properties expected from a well-behaved
real-time rewrite theory. We avoid introducing the accurate definition
of time-robustness, but instead give the following lemma to prove
time-robustness:
\begin{lemma}[\cite{DBLP:journals/entcs/OlveczkyM07a}]
\label{l:timerobustness}
Let $\cal R$ be an object-oriented specification with a standard tick
rule, and let the infinity element \verb|INF| be the only element in
the time domain which is not a normal time value.
%and let the time domain be \emph{linear}.
Then $\cal R$ is time-robust if the following conditions are satisfied
for all appropriate ground terms $t$ and $r,r'$:
\begin{enumerate}
\item
[(i)] \verb|mte(delta(|$t$\verb|,|$r$\verb|))| $=$
\verb|mte(|$t$\verb|) monus |$r$, for all $r\le$
\verb|mte(|$t$\verb|)|, where \verb|monus| is the built-in minus
operation defined on sort \verb|Time|;
